### 2014-03-14 src/analysis.Rnw
udpate

\begin{figure*}[t]
<<op.sample,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.xp.opsel <- o.op.processed
colnames(o.xp.opsel)[colnames(o.xp.opsel)=="power"] <- "num.operators"

ggplot(subset(o.xp.opsel, reduction < 1000), aes(num.operators, reduction, fill=interaction(type,num.operators), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type) + myopts + theme(legend.position="none") + opts(title="opsel(x)")
@
\caption{Operator selection}
\label{fig:xroundsel}
\end{figure*}

>>>>

\begin{figure*}[t]
<<op.sample,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.xp.opsel <- o.op.processed
o.xp.opsel$operators <- 16 - o.xp.opsel$operators
colnames(o.xp.opsel)[colnames(o.xp.opsel)=="operators"] <- "rm.operators"

df <- subset(o.xp.opsel, rm.operators <= 20 & reduction != Inf & type != 'operator' & (type != 'n-selection' | rm.operators < 9))
#ggplot(df, aes(rm.operators, reduction, fill=interaction(type,rm.operators), dodge=type)) +
#  stat_boxplot(geom ='errorbar')+
#  geom_boxplot() + facet_wrap(~type) + myopts +
#  #theme(legend.position="none") +
#  opts(title="opsel(x)")
qplot(rm.operators, reduction, fill=interaction(type,rm.operators), data=df, geom="boxplot", position="dodge") + theme_bw()
@
\caption{Operator selection comparison between n-selection and other selection methods in mutation reduction.  We show only up to 8-selection}
\label{fig:xroundsel}
\end{figure*}
